Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2020-04-07 paper/notes.tex
Correctly invert
Have tweaked params to get fairly good arrangements of the max graph.

Spatial transfer of information in the system can be halted if
$D\rightarrow 0$ and $\gamma_{i,j}\rightarrow 0$.
%$f(\gamma_{i,1},\gamma_{i,2},...,\gamma{i,M})\rightarrow 1$.

This can be achieved with a function of the gammas and rhos:

@@

Where $f_i$ is a function which permits branching far away from a given axon's
target region and tends to zero inside the target region. It represents an
axon's internal `stopping process'. Note that $\tilde{\rho}_j(\mb{x})$ is the
axon's measurement of $\rho_j(\mb{x})$ and may include measurement noise,
$\xi_\rho$: $\tilde{\rho}_j = \rho_j + \xi_\rho$. Given that the morphogen
gradients are orthogonal, $(\tilde{\rho}_1,\tilde{\rho}_2)$ defines a vector
field $\vec{\rho}(\mb{x})$. Similarly, we can combine
$(\gamma_{i,1},\gamma_{i,2})$ into the vector $\vec{\gamma}$.

@@

where $\vec{\gamma}$ gives the location of the peak and the parameter $w$ is
the width of the peak. This is squashed through an inverting sigmoid, with
sharpness parameter $s$:

\begin{equation}\label{eq:f}
f_i\big(\vec{\rho}(\mb{x})\big) = \frac{2}{1 + \mathrm{e}^{-s g_i(\vec{\rho}\,)}} - 1
\end{equation}

@@

\begin{equation}\label{eq:gf}
f_i\big(\vec{\rho}(\mb{x})\big) = \frac{2}{1
+ \mathrm{e}^{-s \mathrm{e}^{-\big(\frac{\vec{\rho}(\mb{x})-\vec{\gamma}}{2 w}\big)^2 } }} - 1
\end{equation}

@@

Reference \cite{goodhill_development_2005} (from which the headings and quotes
below are taken) gives a list of features which a model of retinotectal
dfevelopment or regeneration should address.

@@

\begin{displayquote}
\emph{If a Xenopus presumptive tectum is rotated early enough during devel- opment,
a map is formed that is normal relative to the whole animal, whereas later
rotations lead to a rotated map (Chung \& Cooke 1978).}
\end{displayquote}

>>>>

Spatial transfer of information in the system can be halted if the flux of
axonal branching (the term in brackets) tends to 0.  This can be achieved with
a function of the gammas and rhos:

@@

Where $f_i$ is a function which permits branching far away from a given axon's
target region and tends to zero inside the target region. It represents an
axon's internal `stopping process'. Note carefully that this internal axonal
function does \emph{not} depend directly on space; it is a function of the
interaction parameters $\gamma$ and of the signalling molecule density,
$\rho$. Note that $\tilde{\rho}_j(\mb{x})$ is the axon's \emph{measurement} of
$\rho_j(\mb{x})$ and may include measurement noise, $\xi_\rho$:
$\tilde{\rho}_j = \rho_j + \xi_\rho$. Given that the morphogen gradients are
orthogonal, $(\tilde{\rho}_1,\tilde{\rho}_2)$ defines a vector field
$\vec{\rho}\,(\mb{x})$. Similarly, we can combine $(\gamma_{i,1},\gamma_{i,2})$
into the vector $\vec{\gamma}$.

@@

where $\vec{\gamma}$ gives the location of the peak and the parameter $w$ is
the width of the peak. This is squashed through a sigmoid, with
sharpness parameter $s$ and inverted:

\begin{equation}\label{eq:f}
f_i\big(\vec{\rho}(\mb{x})\big) = 1 - \bigg( \frac{2}{1 + \mathrm{e}^{-s
g_i(\vec{\rho}\,)}} - 1 \bigg)
\end{equation}

@@

\begin{equation}\label{eq:gf}
f_i\big(\vec{\rho}(\mb{x})\big) = 2 - \frac{2}{1
+ \mathrm{e}^{-s \mathrm{e}^{-\big(\frac{\vec{\rho}(\mb{x})-\vec{\gamma}}{2 w}\big)^2 } }}
\end{equation}

@@

Reference \cite{goodhill_development_2005} (from which the headings and quotes
below are taken) gives a list of features which a model of retinotectal
development or regeneration should address.

@@

\begin{displayquote}
\emph{If a Xenopus presumptive tectum is rotated early enough during development,
a map is formed that is normal relative to the whole animal, whereas later
rotations lead to a rotated map (Chung \& Cooke 1978).}
\end{displayquote}
